Consumption and resistance across states

### 2017-02-22 states/resistance/state-report.Rmd
fixed filepaths

```{r load_data}
coherence = read_tsv('../../../../../antibiogram/analysis/geographic-coherence/coherences.tsv') %>%
  rename(resistance_drug=drug) %>%
  mutate(resistance_drug=tolower(resistance_drug),
         state_coherent=level %in% c('state', 'hrr', 'zipcode')) %>%
  select(bug, resistance_drug, state_coherent)

# Antibiogram data, with individual records
abg = read_tsv('../../../../../antibiogram/data/abg.tsv') %>%
  mutate(drug=tolower(drug)) %>%
  rename(resistance_drug=drug) %>%
  select(bug, resistance_drug, state, percent_susceptible)

@@

# State-level consumption data
state_consumption = read_tsv('../../bene-consumption/state_usage_2011.tsv') %>%
  rename(consumption_drug=antibiotic) %>%
  select(state, consumption_drug, cpkp, did)

>>>>

```{r load_data}
coherence = read_tsv('../../../../antibiogram/analysis/geographic-coherence/coherences.tsv') %>%
  rename(resistance_drug=drug) %>%
  mutate(resistance_drug=tolower(resistance_drug),
         state_coherent=level %in% c('state', 'hrr', 'zipcode')) %>%
  select(bug, resistance_drug, state_coherent)

# Antibiogram data, with individual records
abg = read_tsv('../../../../antibiogram/data/abg.tsv') %>%
  mutate(drug=tolower(drug)) %>%
  rename(resistance_drug=drug) %>%
  select(bug, resistance_drug, state, percent_susceptible)

@@

# State-level consumption data
state_consumption = read_tsv('../bene-consumption/state_usage_2011.tsv') %>%
  rename(consumption_drug=antibiotic) %>%
  select(state, consumption_drug, cpkp, did)
